---
title: "My Presentation with Plotly"
author: "Yu Mo"
date: "February 27, 2019"
output: 
  ioslides_presentation
---

<style type="text/css">
body, code.r{
  font-size: 14px;
}
pre {
  font-size: 14px
}
</style>

## IRIS (scatter plot)
#### Data description
<font size="3">The measurements in centimeters of the variables sepal length and width and petal length and width, respectively, for 50 flowers from each of 3 species of iris. The species are Iris setosa, versicolor, and virginica.</font>
```{r message=FALSE,echo=FALSE,fig.height=4, fig.width=7}
library(datasets)
data(iris)
library(plotly)
plot_ly(iris,type="scatter", x= ~Sepal.Length, y= ~Sepal.Width, mode="markers",color=~Species, symbol = ~Species)
```

## Flow of the River Nile (time series plot)
#### Data description
<font size="3">Measurements of the annual flow of the river Nile at Aswan (formerly Assuan), 1871-1970, in 10^8 m^3.</font>
```{r message=FALSE,echo=FALSE,fig.height=4, fig.width=6}
data(Nile)
plot_ly(x=time(Nile), y= Nile, mode = 'lines')
```



